\documentclass[../mcmpaper]{subfiles}
\begin{document}
\section{Introduction}
With the popularization of smart phones and the improvement of mobile payment technology, but existing payment methods of cash payment and physical bus card have some disadvantages,such as inconvenient recharge, easy loss, personal inability to view the card swiping records, cross regional inability to use and other problems in the process of using the bus card. Cash payment brings a lot of inconvenience and increases labor costs, Compared with cash payment and physical bus card swiping, bus mobile payment has gradually come into our sight.
\par
At present, bus mobile payment is generally carried out through a third-party payment platform. Now you need to analyze and evaluate the project.
\par
Question 1: Annex 1 and 2 give the information and data description of some bus payment in a city, and try to analyze the travel payment characteristics of passengers in the city.
\par
Question 2: Try to establish a commercial profit mathematical model of public transport third-party payment platform to quantitatively analyze the revenue, expenditure and profit of public transport third-party payment platform.
\par
Question 3: the data given in question 1 is the data obtained during the trial operation of a quarter of buses and subways after installing mobile payment devices. According to the data in question 1, try to estimate the profitability of all buses in the city after becoming rich through the third platform of public transport.
\par
Question 4: combined with the previous calculation results and conclusions, write a business plan feasibility report within 500 words for the mobile payment company, and give suggestions on the feasibility scheme to increase the company's profits.
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../mcmpaper"
%%% End:
